Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-25 paper/paper.tex
authors

% IEEE Format
\author{
  \IEEEauthorblockN{Maciej Malawski}
  \IEEEauthorblockA{AGH University of Science and Technology\\
Dept. of Computer Science\\
Krakow, Poland; and\\
University of Notre Dame\\
Center for Research Computing\\
111 ITC, Notre Dame, IN, USA\\
Email: mmalawsk@nd.edu}
  \and
  \IEEEauthorblockN{Gideon Juve and Ewa Deelman}
  \IEEEauthorblockA{USC Information Sciences Institute\\
4676 Admiralty Way\\
Marina del Rey, CA, USA\\
Email: \{gideon,deelman\}@isi.edu}
  \and
  \IEEEauthorblockN{Jarek Nabrzyski}
  \IEEEauthorblockA{University of Notre Dame\\
Center for Research Computing\\
111 ITC, Notre Dame, IN, USA\\
Email: naber@nd.edu}}

>>>>

% IEEE Format
\author{\IEEEauthorblockN{Maciej
Malawski\IEEEauthorrefmark{1}\IEEEauthorrefmark{3}, Gideon
Juve\IEEEauthorrefmark{2}, Ewa Deelman\IEEEauthorrefmark{2} and Jarek
Nabrzyski\IEEEauthorrefmark{3}} 
\IEEEauthorblockA{\IEEEauthorrefmark{1}AGH University of Science and
Technology, Dept. of Computer Science, Krakow, Poland, Email:
malawski@agh.edu.pl} 
\IEEEauthorblockA{\IEEEauthorrefmark{2}USC Information Sciences Institute, 4676
Admiralty Way, Marina del Rey, CA, USA, Email: \{gideon,deelman\}@isi.edu} 
\IEEEauthorblockA{\IEEEauthorrefmark{3}University of Notre Dame, Center for
Research Computing, 111 ITC, Notre Dame, IN, USA, Email: naber@nd.edu}
}
